---
title: "Exam3"
author: "Clay Cavanaugh"
date: "7/9/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

1. Clearing the environmment
```{r}
rm(list=ls(all=TRUE))
```

2.TidyCensus package

```{r}
library(tidycensus)
census_api_key("6600d5f356e5e45a3774c978db1bd5acd1fbfd3f", install=TRUE, overwrite= TRUE)
readRenviron("~/.Renviron")
v15 <- load_variables(year = 2015,
                      datase = "acs5")
v10 <- load_variables(year = 2010,
                      datase = "acs5")
library(tidyverse)
inequality_panel <- bind_rows(v10, v15)

estimate <- get_acs(geograph = "state",
                 variables = c(gini = c("B19083_001")),
                 year = 2010)

estimate2 <- get_acs(geograph = "state",
                 variables = c(gini = c("B19083_001")),
                 year = 2015)

library(tidyverse)
inequality_panel2 <- bind_rows(estimate, estimate2)

#renaming estimate as gini
library(data.table)
setnames(inequality_panel2, "estimate", "gini")

#renaming state as well
setnames(inequality_panel2, "NAME", "state")

#adding year variable


#head command
head(inequality_panel2)
```

3. Reshaping the inequality value wide

```{r}
inequality_wide <- 
  inequality_panel2 %>%
  pivot_wider(id_cols = c("GEOID","state", "gini"),
              names_from ="state",
              values_from ="gini")
head(inequality_wide)
```

4. Reshapping back to long

```{r}
inequality_long <- 
  inequality_wide %>%
  pivot_longer(cols = starts_with("GEOID"),
               names_to = "state",
               names_prefix = "state_",
               values_to = "gini",
               values_drop_na = FALSE) %>%
  filter(!(gini==0))

```

5. Showing that both sets have same # of observations

```{r}
head(inequality_long)
head(inequality_wide)
inequality_long
inequality_wide
```

6. Collapsing the inequality_long data frame

```{r}
inequality_collapsed <- 
  inequality_long %>%
  group_by(state,year,GEOID,) %>%
  summarize(across(where(is.numeric), sum)) %>%
  select(-c("moe"))
```

7. Producing a map of the United States

```{r}
# load packages
library(rio)
library(tidyverse)
library(googlesheets4)
library(labelled)
library(data.table)
library(varhandle)
library(ggrepel)
library(geosphere)
library(rgeos)
library(viridis)
library(mapview)
library(rnaturalearth)
library(rnaturalearthdata)
library(devtools)
library(rnaturalearthhires) 
library(raster)
library(sp)
library(sf)
library(Imap)
library(remotes)

#transform to WGS84
inequality_long <- st_transform(inequality_long, "+proj=latlong +ellps=WGS84 +datum=WGS84")

#map of the world package
world <- ne_countries(scale="large", returnclass = "sf")

#US map
us <- ne_countries(continent = "United States",
                       scale = "large",
                       returnclass = "sf")

#final plot
us_map = ggplot() +
  geom_sf(data = united_states) +
  geom_sf(data = sa_nr_collapsed, aes(fill= `Log Value`)) +
  scale_fill_viridis(option = "viridis")
  ggtitle("Gini in the United States") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_void()
```

8. importing GDP data from wdi

```{r}
library(WDI)
gdp_current <- WDI(country= "all",
                   indicator = c("NY.GDP.PCAP.CD"),
                   start = 2006, end = 2007, extra = FALSE, cache = NULL)
```

9. Deflating gdp_current

```{r}
library(WDI)
deflator_data = WDI(country = "all",
                    indicator = "NY.GDP.DEFL.ZS",
                    start = 2010, end = 2010,
                    extra = FALSE, cache = NULL)
gdp_deflated = left_join(x=gdp_current,
                          y=deflator_data,
                          by= "country")
#deflating
gdp_deflated$deflated_amount = gdp_deflated$current_amount/
                                (gdp_deflated$deflator/100)
```

10. The three main components of a shiny app are the user interface, server, and then execution of the app. The user interface involves inputs and outputs, the server involves what R should do with everything you can included in the ouputs. Finally, the execution app runs the app and creates it, and then you can upload it or utillize it. 

11. Reading in pdf file from web

```{r}
library(pdftools)
library(tidyr)
library(tidytext)
library(dplyr)
library(stringr)
library(ggplot2)
mytext=pdf_text(pdf =
"https://pdf.usaid.gov/pdf_docs/PA00TNMG.pdf")
```

12. Converting to data frame called armeniatext

```{r}
mytext
armeniatext <- mytext
armeniatext=as.data.frame(armeniatext)
armeniatext$page=c(1:65)
colnames=(armeniatext)[which(names)(armeniatext)=="armeniatext"] <- "text"
```

13. Tokenizing the data and removing stop words

```{r}
armeniatext <- armeniatext %>%
  unnest_tokens(word,text)

data(stop_words)
armeniatext <- aremniatext %>%
  anti_join(stop_words)
```

14. Top 5 most used words in the report 

```{r}
hqfreq <- armeniatext %>%
  count(word, sort=TRUE)
head(hqfreq)

freq= armeniatext %>%
  group_by(page)
  count(word, sort=TRUE)
head(freq)
```

15. Loading the Billboard hot 100 webpage

```{r}
library(rvest)
library(dplyr)
library(ggplot2)
hot100page <- "https://www.billboard.com/charts/hot-100"
hot100exam <- read_html(hot100page)
hot100exam
str(hot100exam)
```

16. Using rvest to obtain all of the nodes in the webpage

```{r}
body_nodes <- hot100exam %>%
  html_node("body") %>%
  html_children()
body_nodes

body_nodes %>%
  html_children()
```

17. Pulling data on rank, artist, title, and last week

```{r}
rank <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__rank__number')]") %>%
  rvest::html_text()

artist <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__artist')]") %>%
  rvest::html_text()

title <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
                     'chart-element__information__song')]") %>%
  rvest::html_text()

last_week <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//button[contains(@class,
                    'chart-sorter__button')]") %>%
  rvest::html_text()
  
```

